\input{Preamble.tex}
\usepackage[disable]{todonotes}					% Todo Notes
\usepackage[draft]{fixme}
\newcommand{\bycykelwithoutspace}{Aalborg Bycykel}
\newcommand{\bycykel}{\bycykelwithoutspace{ }}

\begin{document}
	\include{Frontpage}
	\newpage\null\thispagestyle{empty}\newpage
	\include{Titlesheet}
	\addtocounter{page}{4}
	\newpage\null\thispagestyle{empty}\newpage
	\input{Foreword.tex}
	\newpage\null\thispagestyle{empty}\newpage
	%1027
	\label{startoftoc}
	\begin{KeepFromToc}
		\tableofcontents
		\newpage\null\thispagestyle{empty}\newpage
		\newpage\null\thispagestyle{empty}\newpage
		\todototoc
		\listoftodos
	\end{KeepFromToc}
	\label{endoftoc}
	
	\chapter{Introduction}
	\input{Src/Introduction}
	\chapter{Analysis}
	This chapter includes analysis of the current system already in place in Aalborg, other existing systems, the problem definition, and general requirements.
	\input{Src/Analysis/CurrentSystem}
	\input{Src/Analysis/ExistingSystems}
	\input{Src/Analysis/ProblemDefinition}
	\input{Src/Analysis/Requirements}
	\input{Src/Analysis/TargetAudience}
	
	\chapter{Suggested Solutions}
	Various suggested extensions for the current system are proposed.
	These solutions are then in turn examined and evaluated, in order to determine if a solution is preferred to others and gives valuable information for the software system.
	An exception to this is the Booking Software examination, which makes a concrete choice on what solution choose.
	\input{Src/SuggestedSolutions/AvailabilityOfBicycles}
	\input{Src/SuggestedSolutions/Lock}
	\input{Src/SuggestedSolutions/BookingSoftware}
	\input{Src/SuggestedSolutions/TrackingOfBicycles}
	\input{Src/SuggestedSolutions/ChosenSolution}
	
	\chapter{Technologies}
	Some background material is needed for the development of a solution and this is examined and discussed. This includes describing the Internet of Things and what issues follow that, a description of the Model-View-Controller pattern used for the website, and AJAX(aka dynamic updating of websites). \fxwarning{Skal ER-Diagram være her?}
	\input{Src/RelevantMaterial/InternetOfThings}
	\input{Src/RelevantMaterial/MVC}
	\input{Src/RelevantMaterial/ajax}
    \input{Src/RelevantMaterial/SOAP}
		
	\chapter{Design}
	This chapter will present the design of the product, where a prototype is created hereafter the ER-diagram of the database is explained.
	\input{Src/Prototypes/prototype}
	\input{Src/RelevantMaterial/ER-Diagram}
	\input{Src/design/administrationTools}
	\input{Src/design/architecture}
	\input{Src/design/station}
	
	\chapter{Implementation Problems}\label{chap:implementationproblems}
	This chapter outlines how we tackle various problems found for implementing the system.
	These problems consists of various scenarios where a decision has to be taken on how this is handled.
	As we do not have a customer, the decisions have been taken ourselves when it was required by a customer, but could be changed in the system if wanted by a future customer. For problems concerning backend system stability, the decisions are up to the developer of the system.
	Additionally, for future work, these decisions could be set as configurable variables on the admin page, letting the customers decide how the system should act in a given scenario.
	\input{Src/Behaviour/problems}
	
	\chapter{Implementation}
	This chapter covers implementation details.
	
	\input{Src/Implementation/UI}
	\input{Src/Implementation/Framework}
	\input{Src/Implementation/Interfaces}
	\input{Src/Implementation/ModelAndModelServices}
	\input{Src/Implementation/Controller}
	\input{Src/Implementation/Views}
	\input{Src/Implementation/googlemapsapi}
	\input{Src/Implementation/AdminPage}
	\input{Src/Implementation/Bicyclestation}
	%\input{Src/Implementation/History}
	
	\chapter{Test}
	In order to verify that the functionality of our system works as intended, we perform unit tests on our code. 
    To test the usability of our system, usability tests are also performed.
	\input{Src/Test/Unittest}
	\input{Src/Test/Usabilitytest}
	
	\chapter{Discussion}
	\chapter{Conclusion}
	
	\afterpage{\thispagestyle{empty}}

	\bibliography{Bibliography}
	
	\label{lastpagewithoutappendix}

	\appendix
	\input{Src/Appendix/website-architecture}
	\input{Src/Appendix/admin}
	\input{Src/Appendix/usability-test}
	\cleardoublepage
	\phantomsection
\end{document}
