\section{Administration}
This page will describe the administrative functionality.

\subsection{GPS Tracking}

\subsection{Usage History}

\subsection{GPS Route History}

\subsection{GPS Booking History}

\subsection{Add/Remove}
This part of the administration site handles the adding and removing of users, bicycles, docks, and stations.

\begin{description}[style=nextline]
\item[Add User] The administrator can add a normal user and set up his or her details or the administrator can add another administrator.
\item[Remove User] Removal of users by the administrator is also provided functionality.
However, while the administrator can remove all other users and administrators he cannot remove himself.
\item[Add Bicycle] Functionality for adding bicycles was added, this requires no information about the bicycle being given.
The reason why no  dock have to be given when adding a bicycle is because the administrators have to insert the bicycle manually into a dock.
\item[Remove Bicycle] While addition of bicycles require no information being provided, removal of bicycles requires providing the id of the bicycle.
This is done since the administrator should have removed the bicycle manually before removing it from the system.
\item[Add Dock] Addition of docks requires the administrator choosing which station to which the dock has to be added.
After adding a dock, the station has to be notified because the database on the station has to be updated.
\item[Remove Dock] Removal of docks requires the administrator choosing which dock at which station to remove from, with the caveat that it only allows removal of docks not currently used.
After removing a dock the station containing the dock has to be notified that the dock have been removed from the station.
\item[Add Station] Adding a station requires information, the name, the coordinates, and the ip address, given that we simulate the stations we also need to notify the station software that a new station has been added, however this is not needed for the final version as ours only work as a prototype.
\item[Remove Station] Removal of station requires the administrator to choose which station that has to be removed.
The administrator will be warned that removing this station will also remove all the docks and detach the bicycles from the removed docks.
In our simulated world the station software also needs to be notified to update the database, just as adding a new station this is not needed for the final version.
\end{description}
See \appref{app:addremove} for a picture of the administration page.