\section{Controller}
This section will show how the controller layer works. 
It will illustrate this by giving an example controller, showing what it looks like and what it does.
An overview is then provided of the rest of the controllers and their functions.
For more detail about the Model-View-Controller architecture, see \secref{sec:mvc}.

In \lstref{lst:homeController}, part of the Home Controller can be seen. 
It defines an `action', this action is what is pointed to by the client. 
For space saving purposes all actions but the index action have been omitted.
The home controller uses two services, StationService, used to retrieve an array of all stations, line 8-9, and BookingService, used to retrieve an array of all active bookings for the currently logged in user, line 11-14. 
This illustrates the general idea behind the separation of the entities (the models) and the services associated with those entities.
It then uses the information loaded by 'including' views, and these views then use the information retrieved for displaying.

\begin{lstlisting}[language=php, label=lst:homeController, caption={Home Controller Class}]
<?php
class Home extends Controller
{
    public function index()
    {
        $this->title = "Home";
        $currentPage = substr($_SERVER["REQUEST_URI"], 1);
        $stationService = new StationService($this->db);
        $stations = $stationService->readAllStations();

        if (Tools::isLoggedIn()) {
            $bookingService = new BookingService($this->db);
            $activeBookings = $bookingService->getActiveBookings($_SESSION["login_user"]);
        }

        require 'application/views/_templates/header.php';
        require 'application/views/home/index.php';
        require 'application/views/_templates/footer.php';
    }
    // [...]
}
\end{lstlisting}

The controllers and their `actions' are as such,

\begin{itemize}
\item Home {\begin{itemize} 
            \item Index -- The homepage and what is shown by default.
            \item Unbook -- For cancelling a booking for the logged in user.
            \item Book -- For arranging a booking for the logged in user.
            \end{itemize}}
\item User {\begin{itemize} 
            \item Index -- Redirects to login page if not logged in, and status page otherwise.
            \item Logout -- For logging out.
            \item Login -- For logging in.
            \item createUser -- For creating a new user.
            \item changePassword -- For changing the password of the logged in user.
            \item editProfile and changeAccountInfo -- For changing email or phone number of the logged in user.
            \item forgotPassword, forgotPasswordForm, resetPassword, and resetPasswordForm -- For resetting a lost password.
            \end{itemize}}
\item About {\begin{itemize} 
            \item Index -- Showing an about page.
            \end{itemize}}
\item Admin {\begin{itemize} 
            \item Index -- Showing a special map for administrative purposes.
            \end{itemize}}
\item Ajax {\begin{itemize} 
            \item Index -- Redirects to status page.
            \item getBicyclePositions -- Get a JSON encoded array of coordinates of all bicycles that have not null coordinates.
            \item getStations -- Get JSON encoded information about stations for dynamic updating.
            \item getFreeDocksList -- Get json encoded information about amount of free docks at all station.
            \end{itemize}}
\end{itemize}

What views look like will be illustrated in the next section.