\input{Preamble.tex}

\author{
  Erik Sidelmann Jensen\\
  \texttt{ejens11@student.aau.dk}
  \and
  Lasse Vang Gravesen\\
  \texttt{lgrave11@student.aau.dk}
  \and
  Dennis Jakobsen\\
  \texttt{djakob11@student.aau.dk}  
}

\title{Data Intensive Systems - Miniproject - Part 3}
\date{}

\begin{document}
	\clearpage\maketitle
	\thispagestyle{empty}
	
	\chapter{DIS Miniproject}
	\section{Task E}
	We defined our multidimensional cube using the following xml:
	\lstinputlisting[language=XML]{fklubdw.xml}
	
	We then could answer the following questions:
	
	\textbf{How much is bought at some point during some day?}
	
	We can answer this by looking at summarized hours, we look at the hours with the most spent.
	
	28,618,675 Ører has been spent at the 12th hour and 20,400,875 Ører has been spent at the 13th hour.
	
	\textbf{How does the amount sold change over time?}
	We can answer this by looking at individual years and how much is spent them on them.
	\begin{table}[H]
	    \begin{tabular}{l|l}
	    Year & Sale Amount \\ \hline
	    1996 & 187,650     \\
	    1997 & 2,359,375   \\
	    1998 & 13,696,025  \\
	    1999 & 15,180,275  \\
	    2000 & 15,763,800  \\
	    2001 & 16,402,075  \\
	    2002 & 19,679,050  \\
	    2003 & 18,017,550  \\
	    2004 & 19,876,325  \\
	    2005 & 17,882,675  \\
	    2006 & 20,225,450  \\
	    2007 & 19,932,050  \\
	    2008 & 61,650      \\
	    \end{tabular}
	\end{table}
	
	\textbf{When is it best to restock, given low activity?}
	
	We can answer this by looking at which hours have the least activity during 8-16.
	
	Those hours are 8 with 9,632,450 and 16 with 9,981,050.
	
	A better way of answering this would be to look at the weekdays too, but we do not have that field.
	
	\textbf{Which product gives the most revenue?}
	\begin{table}[H]
	    \begin{tabular}{l|l}
	    Name               & Sale Amount \\ \hline
	    ½L Vand excl. pant & 66,970,550  \\
	    Øl                 & 20,272,250  \\
	    ½L Matilde cacao   & 19,476,750  \\
	    Kaffe/Choko(1 kop) & 11,578,400  \\
	    Juice              & 8,738,675   \\
	    \end{tabular}
	\end{table}
	
	\textbf{What does the increase in sale for specific products look like over time?}
	See the picture below.
	
	\textbf{Is it worth it to sell soda without deposit(pant)}
	See the picture below.
	
	\textbf{Which member have spent the most?}
	The member that has spent the most is '1704' having spent 1,439,650 Ører.
	See the picture below.
    
    \section{Task F}
\end{document}
