\chapter{Usability Test}\label{app:usability-test}
	The website you are about to test is a site that enables you to book Aalborg city bicycles.
	You will go through different parts of the website, involving booking and status of Aalborg bicycles.
	
	\begin{description}[style=nextline]
		\item[Establish an overview]
			Take your time to get an overview of the website.
		\item[Status for bicycle]
			You consider borrowing a bicycle from Aalborg Banegård, but you are uncertain whether more bicycles are available at the station or not.
		
			Find the amount of available bicycle at the station: "Banegården Busterminal".
		\item[Booking - Login]
			In order to gain access to the booking part of the website, you have to be logged in.
			Luckily you already have a user with the following login information:
			
			\textbf{Username:} testuser
			
			\textbf{Adgangskode:} testpassword
			
			Use the above information to login.
		\item[Booking - Time and booking]
			 Now that you are logged in you are ready to book a bicycle.
			 
			 Book a bicycle for tomorrow at 11:25 a.m.
		\item[Cancel planned booking]
			 You notice there is another booking planned for tomorrow but at 11:45 a.m. at Kunsten.
			 This booking is not necessary and thus you want it cancelled.
			 
			 Cancel the booking tomorrow 11:45 a.m. at Kunsten.
		\item[Examine the booking history]
			You have now booked a bicycle for tomorrow and cancelled another booking.
			However, you are interested in getting an overview of all your bookings, those active and previously used ones.
			
			Find and read the booking history for your profile.
	\end{description}